Dynamic Transition Analysis with TIMES

### 2019-01-10 doc/2019-01-poster/poster.tex
added check marks to table, fixed legend size and references, modified "future work" section
changed take aways
Former-commit-id: a022240e0b5adb30ff79d69cd045c581800357f3 [formerly cb6a761acbf7b95577de4d47115ec0ee6ee86c03]
Former-commit-id: 15e28a4e2c41e5ea2ccff711a62f03041376f32e
added costs plot
Former-commit-id: 0237ea97ae76e97243bca32f2b9ecac32f471b54 [formerly 6b30ab847fc24064a74d4fc9fc1fd31d1c53a2c9]
Former-commit-id: cb897036ac48024a4d5fe52214f7c9949dac626e

%----------------------------------------------------------------------------------------
\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear and mixed-linear algorithms. A user-defined objective 
        function is solved within user defined constraints. \hfill \break

\textbf{Key assumptions:}

@@

@@

         \item \textbf{Hydrogen production:} Steam reforming deployed in 2030. Photocatalytic hydrogen production deployed in 2050, assumed to be cost-competitive with other H$_2$ production technologies. \cite{kato_energy_2016} \cite{acar_comparative_2014} \hfill \break

@@

\textbf{Scenario} & \textbf{Figures}         & \textbf{Conventional}      & \textbf{I$^2$CNER}   & \textbf{New nuclear} \\
                  &                          & \textbf{technology}        &  \textbf{technology} & \textbf{reactors}    \\
1                 & Fig. \ref{s1e}\&\ref{s1c}&        Yes                 &           No         &       Yes            \\ 
2                 & Fig. \ref{s2e}\&\ref{s2c}&        Yes                 &           No         &       No             \\ 
3                 & Fig. \ref{s3e}\&\ref{s3c}&        Yes                 &           Yes        &       Yes            \\ 
4                 & Fig. \ref{s4e}\&\ref{s4c}&        Yes                 &           Yes        &       No             \\
\end{tabular}

@@

\vspace{65 mm}

@@

%----------------------------------------------------------------------------------------
%	TAKE AWAY
%----------------------------------------------------------------------------------------

         \begin{alertblock}{Take Aways}
	\begin{itemize}
                \item Nuclear power has the lowest emissions intensity and it results in the most economical energy supply.

@@

                \item Technologies with the highest impact: nuclear power, offshore wind, photocatalytic H$_2$ generation, solar power
	\end{itemize}
        \end{alertblock}

@@

    \item Making transitions more gradual.

@@

\begin{block}{References}

        {\small\bibliographystyle{unsrt} 
        \bibliography{2019-chaube-i2cner-poster}}
\end{block}

>>>>

%----------------------------------------------------------------------------------------
\begin{block}{Methodology}
        \textbf{The Integrated MARKAL-EFOM System (TIMES)} model generator 
        \cite{loulou_documentation_2005} 
        \cite{seebregts_energy/environmental_2002} optimizes energy systems 
        using linear and mixed-linear algorithms. A user-defined objective 
        function is solved within user defined constraints.\\
\textbf{Key assumptions:}

@@

         \item The cost of fossil fuels, geothermal, hydropower, steam reforming and nuclear is held constant. Variation in costs of wind, solar, and photocatalytic H$_2$ production is given in Fig. \ref{cost}.

@@

         \item \textbf{Hydrogen production:} Steam reforming deployed in 2030. Photocatalytic hydrogen production deployed in 2050, assumed to be cost-competitive with other H$_2$ production technologies. \cite{kato_energy_2016} \cite{acar_comparative_2014} \\

@@

\textbf{Scenario} & \textbf{Figures}         & \textbf{Conventional}      & \textbf{I$^2$CNER}   & \textbf{New nuclear} \\
                  &                          & \textbf{technology}        &  \textbf{technology} & \textbf{reactors}    \\
1                 & Fig. \ref{s1e}\&\ref{s1c}&      \greencheck           &         \xmark       &      \greencheck     \\ 
2                 & Fig. \ref{s2e}\&\ref{s2c}&      \greencheck           &         \xmark       &         \xmark       \\ 
3                 & Fig. \ref{s3e}\&\ref{s3c}&      \greencheck           &      \greencheck     &      \greencheck     \\ 
4                 & Fig. \ref{s4e}\&\ref{s4c}&      \greencheck           &      \greencheck     &         \xmark       \\
\end{tabular}

@@

%\vspace{65 mm}

\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{legend}
%\caption{Legend}
\label{legend}
\end{figure}

@@

%----------------------------------------------------------------------------------------
%	TAKE AWAY
%----------------------------------------------------------------------------------------
\begin{figure}[H] 
\centering
\includegraphics[scale=1.2]{cost}
\caption{Cost variation in solar, wind, and photocatalytic H$_2$ production.}
\label{cost}
\end{figure}
         \begin{alertblock}{Take Aways}
	\begin{itemize}
                \item Nuclear power has the lowest emissions intensity and it results in the most economical energy supply.

@@

                \item Technologies with the highest impact so far: nuclear power, offshore wind, photocatalytic H$_2$ generation, solar power
	\end{itemize}
        \end{alertblock}

@@

    \item Capture realistic, gradual transition behaviour.

@@

\begin{block}{References}
        {\footnotesize\bibliographystyle{ieeetr} 
        \bibliography{2019-chaube-i2cner-poster}}
\end{block}
